### 2024-11-26 paper/paper.qmd
Add model validation scripts
Add model validation scripts

#### Read data ####
start <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
stop <- read_parquet(here::here("data/02-analysis_data/stop.parquet"))
```

>>>>

#### Read data ####
start <- read_parquet(here::here("data/02-analysis_data/start.parquet"))
write_csv(start, file = here::here("data/lalalala.csv"))
stop <- read_parquet(here::here("data/02-analysis_data/stop.parquet"))
```

### 2024-11-26 scripts/05-exploratory_data_analysis.qmd
Add model validation scripts
Add model validation scripts

>>>>

```{r}
md <- readRDS(here::here("models/Spadina_Ave___Harbord_St_-_SMART.rds"))
new_data <- start %>% filter(station_name == "Spadina Ave / Harbord St - SMART")
train <- new_data %>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )
new_data$Predicted <- predict(md, newdata = train)
new_data <- new_data[new_data$count <= 8, ]
ggplot(new_data, aes(x = count, y = exp(Predicted))) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
  labs(
    title = "Scatter Plot of True vs Predicted Values",
    x = "True Values",
    y = "Predicted Values"
  ) +
  theme_minimal()

```{r}
md <- readRDS(here::here("models/Madison_Ave___Bloor_St_W.rds"))
new_data <- start %>% filter(station_name == "Madison Ave / Bloor St W")
train <- new_data %>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )
new_data$Predicted <- predict(md, newdata = train)
new_data$Predicted
new_data <- new_data[new_data$count <= 8, ]
ggplot(new_data, aes(x = count, y = exp(exp(Predicted)))) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
  labs(
    title = "Scatter Plot of True vs b Predicted Values",
    x = "True Values",
    y = "Predicted Values"
  ) +
  theme_minimal()

```
```{r}
md <- readRDS(here::here("models/Galbraith_Rd___King's_College_Rd.rds"))
new_data <- start %>% filter(station_name == "Galbraith Rd / King's College Rd")
train <- new_data %>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )
new_data$Predicted <- predict(md, newdata = train)
new_data <- new_data[new_data$count <= 8, ]
ggplot(new_data, aes(x = count, y = exp(Predicted))) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
  labs(
    title = "Scatter Plot of True vs Predicted Values",
    x = "True Values",
    y = "Predicted Values"
  ) +
  theme_minimal()
```

```{r}
md <- readRDS(here::here("models/Ursula_Franklin_St___Huron_St_-_SMART.rds"))
new_data <- start %>% filter(station_name == "Ursula Franklin St / Huron St - SMART")
train <- new_data %>%
    mutate(
      hour = hour(time),
      day = day(time),
      month = month(time),
      year = year(time)
    )
new_data$Predicted <- predict(md, newdata = train)
new_data <- new_data[new_data$count <= 8, ]
ggplot(new_data, aes(x = count, y = exp(Predicted))) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
  labs(
    title = "Scatter Plot of True vs Predicted Values",
    x = "True Values",
    y = "Predicted Values"
  ) +
  theme_minimal()
```
